Mechanized Denotational Semantics of Gradual Typing using Synthetic Guarded Domain Theory

### 2024-01-19 paper-new/appendix.tex
describe Kleisli action on squares

>>>>

Finally, note that all of these constructions lift to squares in a
double CBPV model since the squares themselves form a CBPV model and
the projection functions preserve CBPV structure. For instance, given a square
$\alpha : l \ltdyn_{F c_o}^{F c_i} l'$ and a horizontal morphism $d : B \rel B'$ of appropriate type, we get a square
\[ \alpha \tok d : l \tok B \ltdyn_{U(c_o \to d)}^{U(c_i \to d)} l' \tok B' \]
